Joshua 2.0: An Open Source Toolkit for Machine Translation \\with Syntax, Semirings and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
added joshua-viz to bibliographies; added a few paragraphs for wmt10 about visualization
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1607 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\section{Visualization}
\todo{jonny}

>>>>

\section{Visualization}

We have introduced tools for visualizing two of the main data structures used
in Joshua \cite{joshua-viz}. Each visualization tool is implemented as a
stand-alone program that hooks into the pipeline, but they are distributed with
Joshua. The first program is a hypergraph visualizer. The user can choose from
a set of input sentences, then call the decoder to build the hypergraph.

The second is a derivation-tree visualizer. Joshua can produce output formatted
as a parse tree, where each nonterminal has been annotated with its source-side
span. The visualizer can read in multiple n-best lists in this format, then
display the resulting derivation trees side-by-side. We have found that
visually inspecting these derivation trees is advantageous in debugging many
grammars.

We would like to add visualization tools for more parts of the pipeline. For
example, a chart visualizer would make it easier for researchers to tell where
search errors were happening during decoding, and why. An alignment visualizer
for aligned parallel corpora might help to determine how grammar extraction 
could be improved.
